---
title: "Author R Packages That Extend The Ready4 Framework"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Author R Packages That Extend The Ready4 Framework}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---
```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```
```{r results='hide', message=FALSE}
library(ready4pack)
```

`ready4pack` is a toolkit for implementing a highly standardised workflow to author R packages that extend the [ready4 framework](https://www.ready4-dev.com/) for open and modular mental health systems models.

`ready4pack` builds on two related toolkits for extending the ready4 framework:

- [ready4fun tools for authoring R package functions](https://ready4-dev.github.io/ready4fun/articles/V_01.html); and 
- [ready4class tools for authoring classes and methods](https://ready4-dev.github.io/ready4class/articles/V_01.html)

`ready4pack` integrates these tools in a common workflow, while adding tools for authoring and documenting R package datasets. A combination of the `ready4_pack_manifest` class and `author` method are used to implement this workflow. This workflow has been used to author all public versions of the ready4 framework R packages available in the [ready4 github repository](https://github.com/ready4-dev).

## Workflow example one

[The program to author and document the ready4show package](https://github.com/ready4-dev/ready4show/blob/main/data-raw/DATASET.R) is relatively simple and authors:

- the `ready4show` package [CITATION](https://github.com/ready4-dev/ready4show/blob/main/inst/CITATION), [DESCRIPTION](https://github.com/ready4-dev/ready4show/blob/main/DESCRIPTION), [LICENSE](https://github.com/ready4-dev/ready4show/blob/main/LICENSE) and [README](https://github.com/ready4-dev/ready4show/blob/main/README.md) files;

- [all files in the `ready4show` package R directory](https://github.com/ready4-dev/ready4show/tree/main/R);

- the `ready4show` package [website](https://ready4-dev.github.io/ready4show/);

- two versions of the `ready4show` package manual - [a slimmed down version for end-users](https://github.com/ready4-dev/ready4show/releases/download/Documentation_0.0/ready4show_User.pdf) and [a more detailed inventory of contents intended for developers](https://github.com/ready4-dev/ready4show/releases/download/Documentation_0.0/ready4show_Developer.pdf);

- an [initial `ready4show` release](https://github.com/ready4-dev/ready4show/releases/tag/Documentation_0.0) for hosting supporting files, the creation of which will trigger archiving on [Zenodo with a `ready4show`  package DOI](https://doi.org/10.5281/zenodo.5644569); and

- an [R-CMD-check continuous integration](https://github.com/ready4-dev/ready4show/actions/workflows/R-CMD-check.yaml) algorithm to be implemented each time a new version of `ready4show` is pushed to the `main` branch of the GitHub source code repository.

## Workflow example two

[The program to author and document the youthvars package](https://github.com/ready4-dev/youthvars/blob/main/data-raw/DATASET.R) is a bit more complex as it includes syntax to create package datasets. In addition to the package datasets, the algorithm creates content corresponding to the previous example, specifically:

- the `youthvars` package [CITATION](https://github.com/ready4-dev/youthvars/blob/main/inst/CITATION), [DESCRIPTION](https://github.com/ready4-dev/youthvars/blob/main/DESCRIPTION), [LICENSE](https://github.com/ready4-dev/youthvars/blob/main/LICENSE) and [README](https://github.com/ready4-dev/youthvars/blob/main/README.md) files;

- [all files in the `youthvars` package R directory](https://github.com/ready4-dev/youthvars/tree/main/R);

- the `youthvars` package [website](https://ready4-dev.github.io/youthvars/);

- two versions of the `youthvars` package manual - [a slimmed down version for end-users](https://github.com/ready4-dev/youthvars/releases/download/Documentation_0.0/youthvars_User.pdf) and [a more detailed inventory of contents intended for developers](https://github.com/ready4-dev/youthvars/releases/download/Documentation_0.0/youthvars_Developer.pdf);

- an [initial `youthvars` release](https://github.com/ready4-dev/youthvars/releases/tag/Documentation_0.0) for hosting supporting files, the creation of which will trigger archiving on [Zenodo with a `youthvars` package DOI](https://zenodo.org/record/5646551); and

- an [R-CMD-check continuous integration](https://github.com/ready4-dev/youthvars/actions/workflows/R-CMD-check.yaml) algorithm to be implemented each time a new version of `youthvars` is pushed to the `main` branch of the GitHub source code repository.

## Future documentation

A more detailed guide to using `ready4pack` will be created in 2022.
